---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ftplottools

<!-- badges: start -->
<!-- badges: end -->

ftplottools is a ggplot2 theme made to match the style and colours of charts created by the Financial Times (FT). The package is built and maintained by FT staff members.

## Installation

If you are an FT employee, you can download ftplottools from our own internal R package repository (FTRAN): 

``` r
install.packages("ftplottools", repos = "https://financial-times.github.io/FTRAN/")
```

If you are not an FT employee, you can download the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Financial-Times/ftplottools")
```
## Example

The following example shows how to apply the FT theme to your ggplot2 object.
The various theme elements can be applied by adding `ft_theme()` to your plot.
Colour scales can be applied by adding `scale_color_ft()` or `scale_fill_ft()`.

```{r example}
library(ftplottools)
library(ggplot2)

ggplot(mpg, aes(displ, hwy, colour = class)) + 
  geom_point() +
  ft_theme() +
  scale_color_ft()
```
If you want to be more specific about the FT colours you choose, you can pick them directly using `ft_colors()`:

```{r}
ggplot(mpg, aes(class, fill = drv)) +
  geom_bar() +
  ft_theme() +
  scale_fill_manual(values = ft_colors("claret", "oxford", "teal"))
```

To see a full list of the available colours along with their labels, call `ft_colors()` (without any arguments).

```{r}
head(ft_colors(), 10)
```

